### 2021-08-12 paper/paper.tex
Add sentence on own time integration schemes
Update Trixi version

Once information about the time span $[0, T]$ is provided, a semidiscretization
in \trixi can be converted into an ODE problem, which can be solved by methods
from OrdinaryDiffEq.jl. The flexible callback infrastructure of this ODE library
allows us to provide extended functionality for \trixi without modifying any
main loop. In particular, various tasks such as input/output operations, adaptive
mesh refinement (AMR), and positivity preserving limiting are implemented using
callbacks.

@@

The most important design decision was to create \trixi as a library. In the
context of simulation-focused scientific computing, there are many (open
or closed source) codes that are designed as monolithic applications that can
simulate a specific setup. These codes can often be configured to a limited extent
by specifying compile time options or editing parameter files. In contrast, users of
\trixi do not need to compile anything or learn parameter file syntax. Instead, they can
just load the library and write their simulation setups in Julia. Scripts that describe
a simulation setup for \trixi are referred to as ``elixirs''. As of version
v0.3.55 (August 2021), \trixi comes with approximately 200 example elixirs. A basic elixir
might look as follows:

>>>>

Once information about the time span $[0, T]$ is provided, a semidiscretization
in \trixi can be converted into an ODE problem, which can be solved by methods
from OrdinaryDiffEq.jl. The flexible callback infrastructure of this ODE library
allows us to provide extended functionality for \trixi without modifying any
main loop. In particular, various tasks such as input/output operations, adaptive
mesh refinement (AMR), and positivity preserving limiting are implemented using
callbacks. In case full control over the time step loop is required, e.g., to experiment with new
features that are not easily realized with the existing API, \trixi also implements its own time
integration schemes that mimic the interface of OrdinaryDiffEq.jl and that can be used as drop-in
replacements.

@@

The most important design decision was to create \trixi as a library. In the
context of simulation-focused scientific computing, there are many (open
or closed source) codes that are designed as monolithic applications that can
simulate a specific setup. These codes can often be configured to a limited extent
by specifying compile time options or editing parameter files. In contrast, users of
\trixi do not need to compile anything or learn parameter file syntax. Instead, they can
just load the library and write their simulation setups in Julia. Scripts that describe
a simulation setup for \trixi are referred to as ``elixirs''. As of version
v0.3.57 (August 2021), \trixi comes with approximately 200 example elixirs. A basic elixir
looks as follows:
